---
title: "At_genome_resources"
author: "Chandler Sutherland"
date: "2024-04-16"
output: html_document
---

Purpose: Let's keep track of the Arabidopsis genomes! Who is sequenced where, and to what depth? 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggplot2)
library(openxlsx)
library(ggvenn)
```
Load datasets from the most recent pangenome pubs, the pan-NLRome paper, and 1001 genomes. 
```{r}
input_path <- "C:\\Users\\chand\\Box Sync\\Krasileva_Lab\\Research\\chandler\\Krasileva Lab\\E14\\e14_R\\At_genome_resources\\"

Kang <- readxl::read_xlsx(path=paste(input_path, 'Kang_2023_metadata.xlsx', sep=''))
Lian <- readxl::read_xlsx(path=paste(input_path, 'Lian_2024_metadata.xlsx', sep=''), sheet=1, skip=2)
Wlod <- readxl::read_xlsx(path=paste(input_path, 'Wlodzimierz_2023_metadata.xlsx', sep=''))
onetusind_genome <- read_csv(file=paste(input_path, '1001_genomes_metadata.txt', sep=''), 
                             col_names=c("accession_id", "sequencer", "name", "Country", "name_2", "Latitude", 
                                         "Longitude", "Collector", 'NA', 'CS_number', 'admixture_group', 'NA_2', 'color_code'))
nlrome <- readxl::read_xlsx(path=paste(input_path, 'NLRome_metadata.xlsx', sep=''))
Jiao <- data.frame(
  stringsAsFactors = FALSE,
            accession = c('An-1', 'C24', 'Cvi-0', 'Eri-1', 'Kyo', 'Ler-0', 'Sha')) %>% 
  mutate(Jiao='TRUE')
```
```{r}
#check overlap between Lian and 1001 genomes

print(paste('There are ', as.character(sum(Lian$Accession %in% onetusind_genome$name)), 'genomes from Lian 2024 in the 1001 genome resource.'))
Lian %>% filter(Accession %in% onetusind_genome$name)
```
Goal dataframe: Accession Name, CS_number if exists, present in 1001 genomes?, present in Lian?, present in Kang?, present in NLRome?, other RNA resource? other long read genome resource? 

```{r}
#use 1001 genome as the backbone dataframe 
thousand <- onetusind_genome %>% subset(select=c(accession_id, name, name_2, CS_number)) %>% mutate(thousand_one = 'TRUE')
nlrome_2 <- nlrome %>% subset(select=c(`Original ID`, `Updated 1001G_ID`, Accession, Stock_Numbers)) %>% mutate(NLRome='TRUE')
Lian_stub <- Lian %>% subset(select=c('Accession')) %>% mutate(Lian='TRUE')
Kang_stub <- Kang %>% mutate(Kang='TRUE')
Wlod_stub <- Wlod %>% subset(select=c('Accession_name')) %>% mutate(Wlod='TRUE')

all_set <- merge(thousand, nlrome_2, by.x='accession_id', by.y='Updated 1001G_ID', all=T) %>% 
  subset(select=c(accession_id, name, CS_number, NLRome, thousand_one)) %>% 
  merge(Lian_stub, by.x='name', by.y='Accession', all=T) %>%
  merge(Kang_stub, by.x='name', by.y='Name', all=T) %>%
  merge(Wlod_stub, by.x='name', by.y='Accession_name', all=T)%>%
  merge(Jiao, by.x='name', by.y='accession', all=T)%>%
  mutate_all(~replace(., is.na(.), FALSE)) 

sequenced <- all_set %>%
  filter(!(NLRome=='FALSE' & Lian == 'FALSE' & Kang=='FALSE')) #remove 1001 genomes not present elsewhere 

sequenced %>% filter(CS_number==`CS Number`) %>% filter(CS_number !='FALSE')
#5 cases where the CS number matches 

sequenced %>% filter(CS_number != 'FALSE' &  `CS Number` != 'FALSE') %>% filter(CS_number != `CS Number`)

not_thousand <- all_set %>% filter(thousand_one=='FALSE')


```




Ok, lots of manual pruning to be done, but a rough venn diagram is doable 

```{r}
x<- list(
  thousand_and_one = all_set %>% filter(thousand_one=='TRUE') %>% pull('name'), 
  nlrome = all_set %>% filter(NLRome=='TRUE') %>% pull('name'),
  Lian = all_set %>% filter(Lian=='TRUE') %>% pull('name'),
  #Kang = all_set %>% filter(Kang=='TRUE') %>% pull('name'), 
  Wlod = all_set %>% filter(Wlod=='TRUE') %>% pull('name')
)

ggvenn(
  x, 
  fill_color = c("#0073C2FF", "#EFC000FF", "#868686FF", "#CD534CFF", 'orange'),
  stroke_size = 0.5, set_name_size = 5
  )
```
```{r}
x<- list(
  #thousand_and_one = all_set %>% filter(thousand_one=='TRUE') %>% pull('name'), 
  nlrome = sequenced %>% filter(NLRome=='TRUE') %>% pull('name'),
  Lian = sequenced %>% filter(Lian=='TRUE') %>% pull('name'),
  Kang = sequenced %>% filter(Kang=='TRUE') %>% pull('name'), 
  Wlodzimierz = sequenced %>% filter(Wlod=='TRUE') %>% pull('name')
)

ggvenn(
  x, 
  fill_color = c("#0073C2FF", "#EFC000FF", "#868686FF", "#CD534CFF", 'orange'),
  stroke_size = 0.5, set_name_size = 5
  )
```

Golden list of genomes:
```{r}
golden_genomes <- all_set %>% filter(thousand_one=='TRUE' & NLRome == 'TRUE') %>% filter(Lian=='TRUE' | Kang=='TRUE' | Wlod=='TRUE' | Jiao =='TRUE')

golden_genome_list <- golden_genomes %>% pull(name)

y<- list(
  Lian = golden_genomes %>% filter(Lian=='TRUE') %>% pull('name'),
  Kang = golden_genomes %>% filter(Kang=='TRUE') %>% pull('name'), 
  Jiao = golden_genomes %>% filter(Jiao=='TRUE') %>% pull('name'),
  Wlodzimierz = golden_genomes %>% filter(Wlod=='TRUE') %>% pull('name')
)

ggvenn(
  y, 
  fill_color = c("#0073C2FF", "#EFC000FF", "#868686FF", "#CD534CFF"),
  stroke_size = 0.5, set_name_size = 3, text_size=3,
  show_elements=F
  )
```
```{r}
final <- golden_genomes %>% pivot_longer(cols=c('Lian', 'Kang', 'Wlod', 'Jiao'), names_to='source') %>% filter(value=='TRUE') %>% subset(select=c('name', 'accession_id', 'CS_number', 'source'))

write.xlsx(final, paste(input_path, 'golden_genomes.xlsx', sep=''))
```

